---
title: "Report"
author: "Raul Vazquez, Gerardo Parrello"
date: "December 14, 2018"
output:
  html_document: default
  pdf_document: default
geometry: "left=1cm,right=1cm,top=2cm,bottom=2cm"
params:
  plot_height: 549
  plot_width: 888
---

```{r setup, include=FALSE, echo=FALSE}
knitr::opts_chunk$set(
  echo = FALSE,
  cache = FALSE
  )
source("./code.R")
```

## Executive Summary
### What is this report about?
Our purpose is to predict profitability for a list of new products based on the performance and characteristics of current products, including in our prediction the product category for each one to asses the impact of specific attributes, customer and service reviews, for certain product types.

### Preamble
From previous analysis, we know that 4 Star Reviews, 2 Star Reviews and Positive Service Reviews are the best predictors of Sales Volume. In this review, we have added Product Type as a possible predictor of Sales Volume.

### Conclusions
After our analysis we conclude that Product Type is not a good predictor of Sales Volume, although that a product pertains to the type 'Game Console' is significant.

We can also say that there is not enough data to asses the impact of customer and service reviews for each product category independently, but we can assert their importance in overall.

Finally, we have included a csv file named *new.csv* with the predicted Sales Volume and Total Profit using our best model.

### Recommendations
Since we do not posses enough data to asses significance of variables for each product category, we recommend regrouping the data by a different categorization which creates bigger but still realistic groups.

## Technical Analysis
```{r results='asis', eval=FALSE}
dfSummary(existingProducts_orig, plain.ascii = FALSE, style = "grid")
```

### Preprocessing
In order to perform modeling over our dataset, we have applied the following transformations:

* Outlier elimination: we have excluded two observations that present Volume over 7000
* Normalization of numerical variables, with exception of the target attribute, using z-transformation
* Feauture selection

#### Feature Selection
In order to assert the importance of variables in respect to Sales Volume and select the most significant, we have run a `r trainedModels[["lm"]]$modelInfo$label` model:
```{r}
summary(trainedModels[["lm"]])
```
From this we reassert our previous conclusion about the significance of 4 Star Reviews and Positive Service Reviews. Nonetheless we find that 2 Star Reviews becomes not significant when introducing Product Type (as dummies), whereas pertaining to category 'Game Console' is now significant.

### Modeling
To predict Sales Volume, we have trained the following models:
```{r echo=FALSE, results='asis'}
for(m in trainedModels){
  cat('\n')
  cat('* ')
  cat(m$modelInfo$label, '\n')
}
```

For performance metrics we have used repeated cross validation of `r cvRepeatNum` repeats over `r cvFoldNum` folds. For optimization we have used a tune lenght of `r tuneLength`.

#### Performance Metrics
Using our performance metrics, we have determined our best model to be `r trainedModels[["rf"]]$modelInfo$label`, as we can see below. Columns marked with * refer to the performance of our models over our testing set; without, over the training set.
```{r}
knitr::kable(
  metricsSet[order(-metricsSet$Rsquared),]
)
```

#### Normalized Error Plots
Below we can see normalized (z-transformed) prediction error over volume for all our models. In orange, observations pertaining to our training set; in blue, to our testing set.
```{r eval=TRUE}
p <- p_grid
p$height <- params$plot_height * 1.6
p$width <- params$plot_width
p
```

```{r eval=FALSE}
p <- p_scatter_type
p$height <- params$plot_height * 1.5
p$width <- params$plot_width
p
```

<!--
Executive Summary

Goal

Este informe contiene dos objetivos principales:
Predecir las ventas de PC, Laptops, Netbooks y Smartphones.
Investigar el impacto que tiene categoría de producto en nuestras ventas.

Highlights

La base de datos de ventas histórica no es lo suficientemente grande como para encontrar patrones y poder predecir con gran confianza.
Si creemos en los resultados podemos concluir que los modelos utilizados predicen muy bien las cantidades bajas de volumen, en contra no existe un modelo que nos prediga eficientemente las cantidades elevadas de volumen.
Las predicciones de nuestras cuatro categorías no son altas, con lo que podemos concluir que las predicciones son bastante acertadas.

Recomendaciones

Ampliar y recolectar más datos de nuestras operaciones con el fin de poder realizar análisis más avanzados y más precisos.
Agrupar los tipo de producto en categorías de producto con el objetivo de visualizar el impacto de estas en Positive Service y Customer Reviews.

Analysis

Nuestro análisis para predecir el volumen de ventas de nuevos productos dónde no tenemos datos, está basado en la idea que los productos actuales comparten atributos con los potenciales nuevos productos.

Las cuatro categorías de producto con mayor potencial de venta son las siguientes, véase lista completa en Anexo.

Methodology

Nuestro análisis para encontrar los mejores predictores para predecir volumen nos ha llevado a escoger las siguientes variables para nuestro análisis: “Positive Service” y “4 star Reviews” para modelar hemos utilizado los siguientes algoritmos de regresión con las siguientes métricas:

KNN
GBT
SVM
RForest

Después de optimizar los modelos con el fin de encontrar las mejores métricas y una performance que se adecuara a lo que buscamos hemos decidido utilizar el KNN, el cual ha sido el que mejor resultados nos ha reportado.

Insertar Métricas y Gráfico de error.
Message Input
-->